FAIR fission track analysis with geochron@home

### 2025-10-03 geochron@home/manuscript/paper.tex
Mentioned student vandalism

The rightmost three columns of Table~\ref{tab:crowdtable} contain
summary statistics ($n_g$, $r_p$ and $s_p$) giving, for each student,
the number of grains counted and the weighted mean and standard
deviation of the ratios of the student's count to PV's count for each
grain (definitions provided in the caption). The true number of tracks
in each ROI is unknown, so we are comparing the students with PV
(remembering that PV's count is also subject to error, which is the
same for each student). $r_p$ measures agreement with PV on average
and $s_p$ measures consistency over grains. For good agreement $r_p$
should be close to 1 and $s_p$ should be small.  Perfect agreement is
$r_p = 1$ and $s_p = 0$. For comparison, an $r_p = 1.04$ and $s_p =
0.69$ is obtained for PV and AC using just the counts in the common
areas $A_0$ from Section~\ref{sec:private}. With the caveat that the
ROIs are different and PV's counts are different, this calculation
shows that there is a group of 6 (possibly 9) students whose agreement
with PV is comparable with AC's. This group does not include student
229 whose $r_p = 0.95$ but with a large $s_p = 1.62$.\medskip

>>>>

The rightmost three columns of Table~\ref{tab:crowdtable} contain
summary statistics ($n_g$, $r_p$ and $s_p$) giving, for each student,
the number of grains counted and the weighted mean and standard
deviation of the ratios of the student's count to PV's count for each
grain (definitions provided in the caption). The true number of tracks
in each ROI is unknown, so we are comparing the students with PV
(remembering that PV's count is also subject to error, which is the
same for each student). $r_p$ measures agreement with PV on average
and $s_p$ measures consistency over grains. For good agreement $r_p$
should be close to 1 and $s_p$ should be small.  Perfect agreement is
$r_p = 1$ and $s_p = 0$. For comparison, an $r_p = 1.04$ and $s_p =
0.69$ is obtained for PV and AC using just the counts in the common
areas $A_0$ from Section~\ref{sec:private}. With the caveat that the
ROIs are different and PV's counts are different, this calculation
shows that there is a group of 6 (possibly 9) students whose agreement
with PV is comparable with AC's. This group does not include student
229 whose $r_p = 0.95$ but with a large $s_p = 1.62$. Students near
the bottom of Table~\ref{tab:crowdtable} have undercounted the samples
by such a large degree that their work can be qualified as
vandalism. Section~\ref{sec:outlook} will suggest strategies to detect
and counteract this type of behaviour.\medskip
